climatrends: Precipitation and temperature indices for climate variability analysis in R

### 2020-04-29 inst/paper/paper.Rmd
29042020

# Implementation

# Application: common beans

@@

# Further development
Integration with other datasets as they become available in `R` via API client packages.

>>>>

# Implementation
Describe the main functions, methods and dependencies.

# Application: common beans
Replicate part of the analysis in van Etten et al [-@vanEtten2019] with the beans data to show how we can use this package to capture the influence of climate variability on crop performance. The idea is to show the same PlackettLuce Tree.

@@

Pick some random points in Norway (or Scandinavia??) and check how the trends on temperature indices over the last 20 years.

# Further development
Integration with other datasets as they become available in `R` via API client packages. New indices related to the physiology of crops to be implemented while I work on the rice data.
